---
title: "Who gets to work from home in Los Angeles County?"
author: "Luke Morris"
format:
  html:
    page-layout: article
editor: visual
---

```{r include=FALSE}
here::i_am("display/charts.qmd", uuid = "3484df9d-ba4e-4349-939b-dbd882d22650")

source(here::here("map/mapplots.R"))
```

Let's take a look at who reported to the [U.S. Census Bureau's 2021 1-year American Community Survey](https://www.census.gov/programs-surveys/acs) that they work from home. We'll see which areas of LA County have the most freedom to work from home, and we'll explore how race and ethnicity play into who reported the ability to work from home across different parts of the county.

```{r, echo=FALSE}
#| fig-height: 8
int_map_laCoWfhOverallProp
```

Note that white-colored areas on the map denote where not enough information was collected to put together a figure.

Now let's see how the racial and ethnic makeup of different areas of the county compare with who has the freedom to work from home there.

::: callout-caution
## Keep in mind

Because the 1-year ACS samples a much smaller slice of the U.S. population than the decennial U.S. Census, the margins of error are quite large, and more work would need to be done to establish statistical significance from these figures.
:::

::: column-screen-inset
::: panel-tabset
## Overall population

```{r, echo=FALSE}
#| fig-height: 8
int_map_laCoRaceProps
```

## Work-from-home population

```{r echo=FALSE}
#| fig-height: 8
int_map_laCoWfhPropByRace
```
:::
:::

Charts put together using `tidycensus` and `plotly`. Inspiration taken from [Matthew Raifman](https://twitter.com/MatthewRaifman/status/1570871070445678600)
